Assessment and Optimization of Nowcast Measures for Trend Detection

### 2024-02-09 sections/04-application.tex
Add first plots for ed arrival application
Update on Overleaf.

Besprechen

\begin{itemize}
    \item Was ist x-calligrafisch? aktuell betrachteter Nowcast oder "bester" Nowcast? Aktuell betrachteter Nowcast (keine "Auswahl" nötig mit Maß, Trainingsdatensatz, Rolling Fit, ...)
    \item Welche Lags werden betrachtet? Tage, Woche(n)
    \item Wie geht man mit missing values um? Vor allem auch für missing values für manche issued-times, wenn es aber andere issed-times gibt, für die Werte vorliegen?
    \begin{itemize}
        \item Imputation (2. Wahl)
        \item Nachgereichte Werte mit ursprünglichen Daten (1. Wahl)
        \item Nachgereichte Werte mit späteren Daten $\rightarrow$ nicht benutzen
    \end{itemize}
\end{itemize}

\subsection{Forecasting emergeny department arrivals}

@@

>>>>

\begin{figure}
    \centering
    \includegraphics{plots/covid_nowcast/00_true_data.pdf}
    \caption{The seven-day-hospitalization of Covid in Germany as reported by the RKI \hl{Add citation}.}
    \label{fig:app-covid-true}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{plots/covid_nowcast/00_nowcast_data.pdf}
    \caption{Nowcast data without removal of outliers}
    \label{fig:app-covid-nowcast}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{plots/covid_nowcast/01_nowcast_data_without_outliers.pdf}
    \caption{Nowcast data after removal of outliers}
    \label{fig:app-covid-nowcast-no-outliers}
\end{figure}

\begin{table}[]
    \centering
    \input{plots/covid_nowcast/01_model_scores}
    \caption{Point evaluation measures for the issued mean of the different models. Note that not for all dates all models issue nowcasts.}
    \label{tab:app-covid-rmse}
\end{table}

\begin{itemize}
    \item Seven-day hospitalization rate as central steering measure for COVID measures in Germany
    \item Describe how it is computed
    \item Outline measures and sources to find methods
    \item Present overall measures for methods (Table~\ref{tab:app-covid-rmse})
    \item Present why trending is important, particularly the differentiation between increase and decrease
    \item Use only a subset of all methods for trending evaluation (best methods)
    \item Present trending of the subset
\end{itemize}
\subsection{Forecasting emergency department arrivals}

@@

\begin{table}
\centering
\input{plots/ed_arrival/accuracies.tex}
\caption{Accuracies (without exclusion area) and RMSE for the considered models in \textcite{Rostami-Tabar2023}}	
\end{table}

\begin{figure}
	\centering
	\includegraphics{plots/ed_arrival/Cond_Prob_lag_3.pdf}
        \caption{Conditional probability plot for ED arrival}
\end{figure}
